Sequential rank agreement methods for comparison of ranked lists

### 2015-04-14 latex/paper.Rnw
Text

\begin{abstract}

\end{abstract}

@@

Ranked lists occur in many applications of statistics. Regression
methods rank predictor variables according to magnitude of association
with outcome, prediction models rank subjects according to their risk
of an event, and genetic studies rank genes according to their
difference in expression across samples. A common research question is
where to stop, \ie, to decide the maximal significant rank.  In the
three examples this would correspond to the number of significantly
associated predictor variables, the number of patients at high risk of
an event, and the number of genes that are worth to pursue in further
experiments, respectively.

@@

The manuscript is ... as follows

>>>>

\begin{abstract}
  The comparison of ranked lists has been studied for several decades
  but since the advent of large data types it has received increased
  interest. Computer science and genomics are just two areas that need
  to compare ranked lists in order to in- vestigate similarities
  between different analytical methods. Often the aim is to find a
  measure of similarity for two or more ordered lists that comprise
  the first k items from each list. Since ordered lists typically are
  more similar at the top of the list another approach, which is taken
  in this paper is to ask: for how long are the lists highly similar?
  Using terminology from agreement analysis we derive the measure
  depth of agreement using the standard deviation of the ranks, a
  method that both provides an intuitive interpretation and can be
  applied to any number of lists even if these are incomplete. The
  finding are illustrated using simulations and applied to a publicly
  available cancer dataset.
\end{abstract}

@@

Ranked lists occur in many applications of statistics. Regression
methods rank predictor variables according to magnitude of association
with outcome, prediction models rank subjects according to their risk
of an event, and genetic studies rank genes according to their
difference in expression across samples.

A common research question is where to stop, \ie, to decide the
maximal significant rank.  In the three examples this would correspond
to the number of significantly associated predictor variables, the
number of patients at high risk of an event, and the number of genes
that are worth to pursue in further experiments, respectively.

@@

The manuscript is organized as follows:
